Hydras \& Co.

### 2023-08-28 doc/chapter-fol.tex

\subsubsection{Rules about the universal quantifier: \texttt{FA1},
\texttt{FA2} and\texttt{FA3}}

@@

The following proof applies \texttt{FA1} in order to build a proof
of \texttt{Prf L [] (t=t)\%fol}  for any $t$\,\footnote{Please note that the quantification on $f$ is \coq's. Thus, \texttt{eq\_ref} is kind of scheme.}

@@

>>>>

\subsubsection{Rules about the universal quantifier: \texttt{FA1},
\texttt{FA2} and \texttt{FA3}}

@@

The following proof applies \texttt{FA1} in order to build a proof
of \texttt{Prf L [] (t=t)\%fol}  for any $t$\,\footnote{Please note that the quantification on $t$ is at the meta-level (\coq's level;
not \texttt{FOL}).}.

Please look also at Figure~\vref{fig:fol-eq-refl}

@@

\begin{figure}[h]
  \centering

\[
  \infer{t=t}{
    \infer[FA1]{(\forall v_0, v_0 = v_0) \,\arrow\, t=t}{}
    &
    \infer[GEN]{\forall v_0, v_0 = v_0}{
      \infer[EQ1]{v_0 = v_0}{}
      }
    }
\]

 \caption{Proof tree of \texttt{(eq\_refl $t$)}}
\label{fig:fol-eq-refl}
\end{figure}

### 2023-08-28 doc/chapter-natural-deduction.tex

@@

In the text, we may use the abbreviation $\Gamma \sdash A$ for
(\texttt{SysPrf $L$ $\Gamma$ $A$}) and
$\sdash A$ for
(\texttt{SysPrf $L$ Empty\_set $A$})

@@

\item $\Gamma, \Delta$ for $\Gamma\cup\Delta$,
\item $A, B, C$ for $\{A, B, C\}$,
\item $\Gamma, A,\dots B$ for $\Gamma\cup\{A \dots B\}$
\item \emph{etc.}
\end{itemize}

\begin{remark}
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from a proof of $X\sdash f$. We only know that such a proof exists, but cannot get it automatically through a \coq function.
\end{remark}

@@

\subsubsection{Examples}

@@

 The library 
 \href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic} contains many derived rules which allow the user to build proofs in a natural deduction style (with introduction and elimination rules).

@@

Let us go on \dots. We leave the completion of the proofs as an exercise. We encourage the reader to write h.er.is own proofs, then compare them with the scripts of \href{../theories/html/hydras.Ackermann.folLogic.html}{folLogic}.

@@

\inputsnippets{folLogic/orI2}

@@

\inputsnippets{folLogic/andE1, folLogic/andE2}

>>>>

In a few words, proving a statement \texttt{SysPrf \_ $T$ $A$} 
is proving the existence of a proof-tree of type \texttt{Prf \textit{Hyp}  $A$}, where \textit{Hyp} is a list of hypotheses all elements of which belong to $T$.

@@

In the text, we may use the abbreviation $T \sdash A$ for
(\texttt{SysPrf $L$ $T$ $A$}) and
$\sdash A$ for
(\texttt{SysPrf $L$ Empty\_set $A$})

@@

\item $T,U$ for $T \cup U$,
\item $A, B, C$ for $\{A, B, C\}$,
\item $T, A,\dots B$ for $T \cup\{A \dots B\}$
\item \emph{etc.}
\end{itemize}

\begin{remark}
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from a proof of $T\sdash f$. We only know that such a proof exists, but cannot get it automatically through a \coq function.
\end{remark}

@@

\subsubsection{Example}

@@

 The library 
 \href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic},
\href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic2} and
\href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic3} contain many derived rules which allow the user to build proofs in a natural deduction style (with introduction and elimination rules).

We present here only a few examples of these rules, the reader
may consult these libraries with \texttt{Search} or by looking 
at the \texttt{coqdoc} generated files. A meta-exercise would be to re-prove a few of these lemmas and/or build an example of application.

@@

@@

@@

%\inputsnippets{folLogic/andE1, folLogic/andE2}

Here are a few examples of looking for rules using \coq's \texttt{Search} command:
